Blum axioms and nondeterministic computation of functions

### 2015-12-16 paper.tex
paper.tex: Explain Hopcroft and Ullman's definition.

\subsection{Hopcroft-Ullman definition}
\subsection{Oded Goldreich definition}
\subsection{Krentel's $\OptP$ class}
\subsection{Valiant's $\#\P$ class}
\subsection{Alternative approaches for nondeterministic functions}

>>>>

\subsection{Hopcroft-Ullman definition}

In their 1979 book,
Hopcroft and Ullman note the need
for defining how a nondeterministic Turing machine can compute a function;
they mention one possible approach \cite[p.~313]{HopcroftUllman1979}:
\begin{quotation}
    We may establish that nondeterministic time and space
    satisfy the axioms if we make an intelligent definition of what it means
    for an NTM to compute a function.
    For example, we might say that $\phi_i(n) = j$
    if and only if there is some sequence of choices by $M_i$ with input $0^n$
    that halts with $0^j$ on the tape,
    and no sequence of choices that leads to halting with some $0^k$, $k \neq j$,
    on the tape.
\end{quotation}
(Hopcroft and Ullman make this definition in the context of integer functions;
in our notation, this means that $\phi_w(x) = y$
if and only if there is some sequence of choices of the machine represented by $w$
when processing the input $x$ that halts with $y$ in the tape,
and no other sequence of choices that leads to halting does so with some $z$,
$z \neq y$, on the tape.)

\subsection{Oded Goldreich definition}
\subsection{Krentel's $\OptP$ class}
\subsection{Valiant's $\#\P$ class}
\subsection{Alternative approaches for nondeterministic functions}
